The Hydrogen Epoch of Reionization Array (HERA)

### 2015-11-04 manuscript.tex
fixed error in channel number, updated wedge fig and added config fig

\begin{figure}[t]
\includegraphics[width=\textwidth]{plots/wedge.png}
\caption{Cartoon of the wedge.  The gray rectangle represents the smooth-spectrum foregrounds as they would be if the instrument had a perfect achromatic response.  The pink wedge area shows the chromatic response of the interferometer, where additional power is thrown up from the gray region to higher k-values with increasing baseline.  The additional horizontal pink line illustrates the affect that other systematics, such as reflections on cables, can have in contaminating the measurement.  The white region shown the 'eor window', where the measurement is not contaminated by foregrounds or systematics.
\label{fig:wedge}}
\end{figure}

@@

\subsection{Delay-Spectrum Approach}
\label{sec:delayapproach}
Given that the response of an interferometer natively measures the power in Fourier modes of the sky within its beam, we see that it is a natural instrument to use for this measurement.  There are now numerous papers in the literature the technique of measuring the power spectrum using an interferometer and the attendant issues (list of citations).  Below, a high-level overview based on  \cite{2012ApJ...756..165P} will be presented. The so-called delay-spectrum approach leverages this response to optimize sensitivity to the desired modes while rejecting modes contaminated by the foreground power in the wedge.  Other than handling overlapping bins in {\em uv} space, the delay-spectrum approach does not combine baselines before squaring and calculating the power spectrum.

@@

The scientific requirement on channel bandwidth is to allow access to k-modes of XXX 5? h/Mpc [ref], which is easily accomplished by as few as 64 channels over the 100 MHz bandwidth.  However, in order to handle radio frequency interference as well as to allow the bandwidth to be characterized a specification of 1024 channels has been set.  This yields a channel bandwidth of 97.7 kHz.

@@

The minimum baseline is set such that the baseline has negligible impact on the minimum baseline (shown in Fig. \ref{fig:kperf} in the standard analysis.  Somewhat arbitrarily, a maximum shortest baseline with equal contribution to $k_{min}$ at the full bandwidth of 100 MHz is chosen, which corresponds to about 15m.  Additionally, this baseline has been well-studied by the PAPER array (ref).

The above requirements also drive the specification on the element diameter, as well as the desire to maximize sensitivity.  This means that the diameter should be something around 15m (that is, a fully filled aperture for the minimum baseline) with a short focal length.

@@

\subsection{Cost}
\begin{figure}[t]
\centerline{
\includegraphics[width=7.5cm]{plots/costfigNew.png} 
}
\caption{\small Costing model for a fixed sensitivity system as a function of diameter (thick blue line and left axis) as well as the round-trip delay for 1,2 and 3 feed-vertex trips (dashed red lines and right axis).  The 60 ns spec is indicated by the horizontal dash line, and the two-trip intersection at about 14-meter is the vertical dashed line.
\label{fig:costfig}}
\end{figure}

@@

\subsection{Configuration}
\label{sec:config}

>>>>

\begin{figure}[t]
\includegraphics[height=3in]{plots/wedge.png}
\caption{Cartoon of the wedge.  The gray rectangle represents the smooth-spectrum foregrounds as they would be if the instrument had a perfect achromatic response.  The pink wedge area shows the chromatic response of the interferometer, where additional power is thrown up from the gray region to higher k-values with increasing baseline.  The additional horizontal pink line illustrates the affect that other systematics, such as reflections on cables, can have in contaminating the measurement.  The white region shown the 'eor window', where the measurement is not contaminated by foregrounds or systematics.
\label{fig:wedge}}
\end{figure}

@@

\subsection{Delay-Spectrum Approach}
\label{sec:delayapproach}
Given that the response of an interferometer natively measures the power in Fourier modes of the sky within its beam, we see that it is a natural instrument to use for this measurement.  There are now numerous papers in the literature the technique of measuring the power spectrum using an interferometer and the attendant issues (list of citations).  Below, a high-level overview based on  \cite{2012ApJ...756..165P} will be presented. The so-called delay-spectrum approach leverages this response to optimize sensitivity to the desired modes while rejecting modes contaminated by the foreground power in the wedge.  Other than potentially handling overlapping bins in {\em uv} space, the delay-spectrum approach does not combine baselines before squaring and calculating the power spectrum.

@@

The scientific requirement on channel bandwidth is to allow access to k-modes of greater than 1 h/Mpc [ref], which requires about 256 channels over the 100 MHz bandwidth.  However, in order to handle radio frequency interference as well as to allow the bandpass to be characterized, a specification of 1024 channels has been chosen.  This yields a channel bandwidth of 97.7 kHz.

@@

The minimum baseline is set such that the baseline has negligible impact on the minimum $k_{bin}$ (shown in Fig. \ref{fig:kperf}) in the standard analysis.  Somewhat arbitrarily, a maximum shortest baseline with equal contribution to $k_{min}$ at the full bandwidth of 100 MHz is chosen, which corresponds to about 15m.  Additionally, this baseline has been well-studied by the PAPER array (ref).

The above requirements also drive the specification on the element diameter, as well as the desire to maximize sensitivity.  This means that the diameter should be something around 15m (that is, a fully filled aperture for the minimum baseline) with a short focal length.  This is revisited in Sec \ref{sec:cost}.

@@

\subsection{Cost}
\label{sec:cost}
\begin{figure}[t]
\centerline{
\includegraphics[width=7.5cm]{plots/costfigNew.png} 
}
\caption{\small Costing model for a fixed sensitivity system as a function of diameter (thick blue line and left axis) as well as the round-trip delay for 1,2 and 3 feed-vertex trips (dashed red lines and right axis).  The 60 ns spec is indicated by the horizontal dash line, and the two-trip intersection at about 14-meter is the vertical dashed line.
\label{fig:costfig}}
\end{figure}

@@

\subsection{Configuration}
\label{sec:config}
\begin{figure}[t]
\centerline{
\includegraphics[width=7.5cm]{plots/config.png} 
}
\caption{\small Config
\label{fig:config}}
\end{figure}
